A Hierarchical Bayesian Framework for Inferring the Stellar Obliquity Distribution

### 2023-03-23 src/tex/ms.tex
[showyourwork] overleaf sync

In this section, we find the expression of $\lambda$ or $i_\star$ in terms of $\psi$, $\theta$, and $i_{\rm orb}$. To do so, we introduce two coordinate systems that describe the stellar spin axis $\vb{n_\star}$ and its planet's orbital axis $\vb{n_{\rm orb}}$, shown in Figure~\ref{fig:coord}.

In the $\{\psi, \theta\}$ coordinate system, we assume the planetary orbital axis is aligned with the $\vb{z}$-axis. The stellar spin axis can be written as 
\begin{equation}
    \vb{n_\star} = \sin{\psi}\cos{\theta}\vu*{x} + \sin{\psi}\sin{\theta}\vu*{y} + \cos{\psi}\vu*{z}
\end{equation}

In the $\{\lambda, i_\star\}$ coordinate system, where the $\vb{x'}$-axis is defined by the observer's line of sight, the stellar spin axis could be written as 
\begin{equation}
    \vb{n_\star}' = \cos{i_\star}\vu*{x}' + \sin{i_\star}\sin{\lambda}\vu*{y}' + \sin{i_\star}\cos{\lambda}\vu*{z}'
\end{equation}

>>>>

In this section, we find the expression of $\lambda$ or $i_\star$ in terms of stellar obliquity $\psi$, the azimuthal angle of the stellar spin axis relative to the orbital axis $\theta$, and the orbital inclination $i_{\rm orb}$. In Figure~\ref{fig:coord}, we introduce two coordinate systems that describe the stellar spin axis $\vb{n_\star}$ and its planet's orbital axis $\vb{n_{\rm orb}}$.

In the $\{\psi, \theta\}$ coordinate system, we assume the planetary orbital axis is aligned with the $\vb{z}$-axis. The stellar spin axis can be written as 
\begin{equation}
    \vb{\hat{n}_\star} = \sin{\psi}\cos{\theta}\vu*{x} + \sin{\psi}\sin{\theta}\vu*{y} + \cos{\psi}\vu*{z}
\end{equation}

In the $\{\lambda, i_\star\}$ coordinate system, where the $\vb{x'}$-axis is defined by the observer's line of sight, the stellar spin axis could be written as 
\begin{equation}
    \vb{\hat{n}_\star}' = \cos{i_\star}\vu*{x}' + \sin{i_\star}\sin{\lambda}\vu*{y}' + \sin{i_\star}\cos{\lambda}\vu*{z}'
\end{equation}
